### 2022-06-19 manuscript.Rmd
Update manuscript.Rmd
Added a paragraph under ### Assessing Estimation Results

The EM algorithm needs starting values for each parameter it wants to estimate. 
If it were provided a single starting value for each parameter, 
the EM optimizer would be at risk of finding a local optimum instead of the global optimum. 
In other words, it would converge on a suboptimal solution resulting in biased parameter and model fit estimates. 
To prevent this, we should give the algorithm a sufficiently large set of random starting values for each parameter in order to maximize our chances of finding the deepest valley that is the global optimum (McLachlan & Peel, 2004). Furthermore, we should ensure the number of initial stage iterations is large for optimization to be successful (Geiser, 2012).

@@

@@

>>>>

The EM algorithm needs starting values for each parameter it wants to estimate. 
If it were provided a single starting value for each parameter, 
the EM optimizer would be at risk of finding a local optimum instead of the global optimum. 
In other words, it would converge on a suboptimal solution resulting in biased parameter and model fit estimates. 
To prevent this, we should give the algorithm a sufficiently large set of random starting values for each parameter in order to maximize our chances of finding the deepest valley that is the global optimum (McLachlan & Peel, 2004). Also, we should ensure the number of initial stage iterations is large for optimization to be successful (Geiser, 2012).

@@

An important outcome of LCA are unconditional class probabilities. These communicate the probability that an individual belongs to each class. A limitation is that our final class solution need not reflect true class membership. Once we do accept a particular class solution, special care also needs to be taken when naming the classes. Class names should be chosen to accurately reflect group membership. Overly simplified and generalized class names may prove misleading to both audiences and researches alike leading to what is known as a naming fallacy (Weller, Bowen & Faubert, 2020).

@@

Among studies using LCA, reporting practices vary significantly (Weller, Bowen & Faubert, 2020).
